Reproduce the analysis and regenerate the manuscript

### 2021-12-07 reproduce_analysis_and_manuscript.Rmd
finishing touches

# for figure 4
library("getDEE2") 
library("DESeq2")
library("clusterProfiler")
library("mitch")
library("kableExtra")
library("eulerr")
library("kableExtra")
library("beeswarm")

>>>>

# for figure 4
library("getDEE2") 
library("DESeq2")
library("clusterProfiler")
library("mitch")
library("eulerr")
library("beeswarm")
